---
title: "Get Started"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(gior)
```

`gior` provides a very simple, straightforward API; initialise your globe with `gior`, then add select your data with `g_data`. For testing purposes the package comes with sample data.

```{r}
data("country_data")

knitr::kable(head(country_data)) # sample data
```

Use [ISO 3166](https://en.wikipedia.org/wiki/ISO_3166-1) Alpha-2 codes, i.e.: United States of America = US.

```{r}
country_data %>% # pipe the data
  gior() %>% # initialise
  g_data(from, to, value) # select columns
```

Then simply customise the appearance with:

- `g_color`
- `g_control`
- `g_brightness`

Or use one of the 13 built-in styles with `g_style`, see `?g_style` for the full list. Note that you can also change the country initally selected.

```{r}
country_data %>% 
  gior(init.country = "ET") %>% # Ethiopia selected
  g_data(from, to, value) %>% 
  g_style("sunset")
```
